\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
Avoiding starting a word with verbatim so spacing is correct
in previous way, we have the . and the R of registry almost on top of each
other and it looks bad
delete word

%%%%%%%%%%%%%%%%%  Internal data representation
The internal data representation closely follows the structure of GDML. A \verb|Registry| class aggregates Python ordered dictionaries that are  used to store the main 
elements of a GDML file. As a \PYGEOMETRY{} user instantiates the geometry the registry is correspondingly updated. When a user is finished with the geometry, the registry 
can be written to disk as a GDML file. \verb|Registry| instances can be aggregated to form a composite geometry or volumes can be removed and added.

@@

%%%%%%%%%%%%%%%%%  Replica, division, parametrised and looped volumes
A powerful feature of Geant4 and hence GDML is the ability to either repeat, divide or parametrise geometry. The class which enables the creation of 
multiple replicas of a volume in a Cartesian, cylindrical or spherical grid is known as a Replica Volume. A Division Volume breaks a primitive into segments 
in either a Cartesian or cylindrical polar coordinates. A parametrised volume allows for the arbitrary multiple placement of solids where the parameters are 
allowed to vary for each placement.  Another way in GDML to create parametrised solids or volumes is GDML loops, where sections of GDML are allowed 
to be repeated with varying parameters. GDML loop loading and expansion are not supported by \PYGEOMETRY{} and will be implemented in a 
future release.

>>>>

%%%%%%%%%%%%%%%%%  Internal data representation
The internal data representation closely follows the structure of GDML. A \verb|Registry| class aggregates Python ordered dictionaries that are  used to store the main 
elements of a GDML file. As a \PYGEOMETRY{} user instantiates the geometry the registry is correspondingly updated. When a user is finished with the geometry, the registry 
can be written to disk as a GDML file. Multiple \verb|Registry| instances can be aggregated to form a composite geometry or volumes can be removed and added.

@@

%%%%%%%%%%%%%%%%%  Replica, division, parametrised and looped volumes
A powerful feature of Geant4 and hence GDML is the ability to either repeat, divide or parametrise geometry. The class which enables the creation of 
multiple replicas of a volume in a Cartesian, cylindrical or spherical grid is known as a Replica Volume. A Division Volume breaks a primitive into segments 
in either Cartesian or cylindrical polar coordinates. A parametrised volume allows for the arbitrary multiple placement of solids where the parameters are 
allowed to vary for each placement.  Another way in GDML to create parametrised solids or volumes is GDML loops, where sections of GDML are allowed 
to be repeated with varying parameters. GDML loop loading and expansion are not supported by \PYGEOMETRY{} and will be implemented in a 
future release.
